Single-step Hybrid Predition

### 2016-12-05 reports/index.Rmd
Remove conclusions from reports
Investigate kernel coefficients for single step predictions

@@

Chapter \@ref(conclusions-and-outlook) provides a summary of the analyses and 
provides an outlook for future analyses.

>>>>

Chapter \@ref(predictor-subsetting) introduces the different predictor sets that
were used for predictions.

Chapter \@ref(kernel-inspection) gives the distribution of coefficients in the 
different kernel matrices used in hybrid prediction.

@@
